Truthfulness Verification System

### 2011-03-30 proposal/paper.tex
Some more cosmetic changes

\begin{lstlisting}[label=Opensearch Protocol, caption=Result using Opensearch]
[
    * "Forrest Gump"
      [
          o "Forrest Gump"
          o "Forrest Gump (character)"
          o "Forrest Gump (novel)"
          o "Forrest Gump (soundtrack)"
          o "Forrest Gump – Original Motion Picture Score"
          o "Forrest Gump (disambiguation)"
      ]
]

@@

Following are a few high priority bugs we are working on

\begin{itemize}
\item Better matching: We tried two ways to match the DU-s in the returned results, one a conservative approach that would try to tokenize so that abbreviations like "U.S.A" and monetary amounts like "\$23.00" are kept as tokens. In the more relaxed approach the tokens were all lowercased and split by spaces. This obviously is the most crucial part of the entire process and it appears we should have separate strategy based on the data type of the doubt unit.
\item Building the classifier: We got the data from TREC 9, which is in a question answer format and have finished converting 100 of the 711 sentences all to statement form with correct answers. Once we have some more sentences labeled we will use it to train a classifier from the features extracted above.
\end{itemize}

>>>>

\begin{lstlisting}[label=Opensearch Protocol, caption=Result using Opensearch]
    * "Forrest Gump"
          o "Forrest Gump"
          o "Forrest Gump (character)"
          o "Forrest Gump (novel)"
          o "Forrest Gump (soundtrack)"
          o "Forrest Gump – Original Motion Picture Score"
          o "Forrest Gump (disambiguation)"

@@

The following are the immediate concerns 
\begin{itemize}
\item Better matching: We tried two ways to match the DU-s in the returned results, one a conservative approach that would try to tokenize so that abbreviations like "U.S.A" and monetary amounts like "\$23.00" are kept as tokens. In the more relaxed approach the tokens were all lowercased and split by spaces. This obviously is the most crucial part of the entire process and it appears we should have separate strategy based on the data type of the doubt unit.
\item Building the classifier: We got the data from TREC 9, which is in a question answer format and have finished converting 100 of the 711 sentences all to statement form with correct answers. Once we have some more sentences labeled we will use it to train a classifier from the features extracted above.
\end{itemize}

\subsubsection{Data Description}
The attached file shows the data collected for each sentence from wikipedia. We take the top 10 results returned by searching wikipeida, and calculate the values mentioned above. "S" denotes that $DU$ appears in the snippet, "T", shows that it appears in the Title, and "N" means the $DU$ was not found anywhere. The other values are separated by ';' are title weight,snippet weight,overall result weight.
